diffusion, websites with 1 pc

### 2023-03-21 src/level_lisa_la.Rmd
level_lisa_la.Rmd

```{r}
firms <- read_csv("https://www.nomisweb.co.uk/api/v01/dataset/NM_142_1.data.csv?geography=1811939329...1811939332,1811939334...1811939336,1811939338...1811939428,1811939436...1811939442,1811939768,1811939769,1811939443...1811939497,1811939499...1811939501,1811939503,1811939505...1811939507,1811939509...1811939517,1811939519,1811939520,1811939524...1811939570,1811939575...1811939599,1811939601...1811939628,1811939630...1811939634,1811939636...1811939647,1811939649,1811939655...1811939664,1811939667...1811939680,1811939682,1811939683,1811939685,1811939687...1811939704,1811939707,1811939708,1811939710,1811939712...1811939717,1811939719,1811939720,1811939722...1811939730,1811939757...1811939767&date=latestMINUS10&industry=37748736&employment_sizeband=0&legal_status=0&measures=20100") %>% 
  select(GEOGRAPHY_CODE, OBS_VALUE) %>% #GEOGRAPHY_NAME, 
  rename(ladcd = GEOGRAPHY_CODE,
         firms = OBS_VALUE)

df <- df %>% left_join(firms) %>% 
  mutate(n_by_firm = n/firms) %>% # N websites/firm
  #filter(!is.na(firms)) %>% 
  select(-n, -firms) %>% 
  rename(n = n_by_firm)

@@

for (t in 1996:2012){
  model <- lm(log(density+0.001) ~ log(London), data = df[df$year==t,])
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.London <- rbind(r2, dens.London)

>>>>

```{r}
firms <- read_csv("https://www.nomisweb.co.uk/api/v01/dataset/NM_142_1.data.csv?geography=1811939329...1811939332,1811939334...1811939336,1811939338...1811939428,1811939436...1811939442,1811939768,1811939769,1811939443...1811939497,1811939499...1811939501,1811939503,1811939505...1811939507,1811939509...1811939517,1811939519,1811939520,1811939524...1811939570,1811939575...1811939599,1811939601...1811939628,1811939630...1811939634,1811939636...1811939647,1811939649,1811939655...1811939664,1811939667...1811939680,1811939682,1811939683,1811939685,1811939687...1811939704,1811939707,1811939708,1811939710,1811939712...1811939717,1811939719,1811939720,1811939722...1811939730,1811939757...1811939767&date=latestMINUS10&industry=37748736&employment_sizeband=0&legal_status=0&measures=20100") %>% 
  dplyr::select(GEOGRAPHY_CODE, OBS_VALUE) %>% #GEOGRAPHY_NAME, 
  rename(ladcd = GEOGRAPHY_CODE,
         firms = OBS_VALUE)

df <- df %>% left_join(firms) %>% 
  mutate(n_by_firm = n/firms) %>% # N websites/firm
  #filter(!is.na(firms)) %>% 
  dplyr::select(-n, -firms) %>% 
  rename(n = n_by_firm)

@@

for (t in 1996:2012){
  model <- lm(log(n+0.001) ~ log(London), data = df[df$year==t,]) #density
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.London <- rbind(r2, dens.London)
